---
title: "OLPS"
author: "ngloe"
date: "17.03.2015"
output: 
  md_document:
    variant: markdown_github
bibliography: OLPS.bib
---

# OLPS  -  On-line Portfolio Selection
The OLPS package provides different On-line Portfolio Selection algorithms
and functions to deal with the on-line portfolio selection problem where a portfolio is rebalanced in every period to achieve certain goals, e.g. maximizing terminal wealth. Datasets to test portfolio selection algorithms are also included.   

For a background on On-line Portfolio Selection see for example [@LH14; <http://arxiv.org/pdf/1212.2129.pdf>]. 

## Features
#### On-Line Portfolio Selection algorithms:
* Buy-and-Hold
* Buy-and-Hold best
* Constant Rebalanced Portfolio
* Best Constant Rebalanced Portfolio
* Universal Portfolio [@Cov91]
* Exponential Gradient [@HSS98]
* Successive Constant Rebalanced Portfolio [@GS00]
* Anticor [@BEG04]
* Passive Aggressive Mean Reversion [@LZH12]
* Volatility Timing [@KO12]

#### Functions:
* transform asset prices into returns (price relatuives)
* transform returns (price relatuives) into asset prices
* calculate portfolio wealth of rebalanced portfolios
* transform a sequence of price relatives into a Kelly market sequence
* projection onto a simplex
* ...

#### Datasets:
* NYSE dataset [used by @Cov91, @HSS98, ...]
* DAX dataset
* DJIA dataset [used by @BEG04, ...]


## Installation
To install the OLPS package run:
```{r eval=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("ngloe/OLPS")
```

## Getting started
Once installed, the package can be loaded using:
```{r eval=FALSE}
library(OLPS)
```

To test portfolio selection algorithms some return data is loaded using the NYSE dataset. We select two assets, *kinar* and *iroqu*:
```{r eval=TRUE, echo=FALSE}
library(OLPS)
```
```{r eval=TRUE, echo=TRUE}
data(NYSE)
x = cbind(kinar=NYSE$kinar, iroqu=NYSE$iroqu)
```

Algorithms can be computed by applying *alg_ALG* on the selected data where *ALG* is the desired algorithm. For example, to approximate the *Universal Portfolio* algorithm (UP) type:
```{r eval=TRUE}
UP = alg_UP(x); UP
```
Accessing UP then returns a short summary of the algorithm's output. To access the calculated portfolio wealth or the portfolio weights you can type:
```{r eval=FALSE}
UP$Wealth
UP$Weights
```
The achieved portfolio wealth (performance) can be plotted by:
```{r eval=FALSE}
plot(UP)
```
To easily compare different algorithms pass them to the plot function:
```{r eval=TRUE}
BH_Market = alg_BH( x, weights=c(0.5, 0.5) )
BH_best   = alg_BHbest(x)
plot(BH_Market, BH_best, UP)
```


## Getting Help
For more details and an overview of the implemented algorithms and functions please refer to the package help by typing:
```{r eval=FALSE}
help(package="OLPS")
```


## References
